Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd

---
```{r setup, include=FALSE}
# Import packages
library(tidyverse)
library(ggplot2)
library(GGally)
library(knitr)
library(boot)
library(caret)
library(randomForest)
library(e1071)
library(class)
set.seed(420)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 14, fig.height = 8)
```
```{r}
#install.packages("kknn")
```

>>>>

---
```{r setup, include=FALSE}
# Import packages
library(tidyverse)
library(ggplot2)
library(GGally)
library(knitr)
library(boot)
library(caret)
library(randomForest)
library(e1071)
library(class)
set.seed(420)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 14, fig.height = 8)
```
